\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[a4paper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\newcommand*\sepline
{
  \begin{center}
    \rule[1ex]{.7\textwidth}{.5pt}
  \end{center}
}

\title{Study Plan for Thesis}
\author{Gurjot Singh}

\begin{document}

\maketitle

\sepline

\section{Chapter 1}

\sepline

\section{Chapter 2}


\sepline

\section{Chapter 3}

\subsection{Model Hamiltonian}

\begin{itemize}
    \item HDvV Hamiltonian
    \item Spin Hamiltonian
    \begin{itemize}
        \item Focus on Zeeman
        \item Study other stuff
    \end{itemize}
\end{itemize}

\subsection{EPR and g-tensor}

\begin{itemize}
    \item Read up on EPR theory
    \item Know what the direction vector of the $g$-tensor signal is.
\end{itemize}

\sepline

\section{Chapter 4}

\begin{itemize}
    \item Mention how this study demonstrated that computational chemistry is about finding balance between accuray and computational cost.
\end{itemize}

\subsection{BS DFT}

\subsection{CASSCF}

\begin{itemize}
    \item Pipek-Mezey localization scheme for double-shell orbs.
\end{itemize}

\subsection{DDCI}

\begin{itemize}
    \item Know the difference between DDCI1, DDCI2 and DDCI3.
    \item Read about $T_{sel}$ parameter.
\end{itemize}

\subsection{BS Coupled Cluster}

\begin{itemize}
    \item Need to read on the CC ansatz and how it works.
    \item Know the difference between CCSD and CCSD(T).
    \item Read local methods and how they work.
    \item Difference between LPNO and DLPNO.
    \item Difference between all the parameters in LPNO approx: $T_{\text{CutPNO}}$, $T_{\text{CutPair}}$ and the 3rd one. (see ORCA docs)
\end{itemize}

\sepline

\section{Chapter 5}

\subsection{Experimental UV-Vis}

\begin{itemize}
    \item Read up on UV-Vis spectroscopy.
    \item Beer-Lambert law.
    \item intermediate \textbf{1} and \textbf{2} were in equillibrium at 233 Kelvin. Read up how equillibrium const are calculated.
\end{itemize}

\subsection{Experimental EPR}

\begin{itemize}
    \item You know epr well enough, especially for $g$-tensors.
    \item Difference between frozen and solution based EPR spectra.
    \item Read up on hyperfine coupling constants.
    \item hyperfine coupling change with lewis acid.
\end{itemize}

\subsection{XANES and TD-DFT}

\begin{itemize}
    \item Read up on XANES/X-ray spectroscopy.
    \item TD-DFT, know a little bit about how it works.
\end{itemize}

\sepline

\section{Chapter 6}

\sepline

% end of document

\end{document}